Abstract Binding Trees

### 2015-10-30 paper.tex
Describe relative monads as skew monoids

\begin{remark}
  A \emph{relative monad} on a functor $\Of{J}{\mathbf{J}\to\mathbf{C}}$ is a
  monoid in the functor category $\mathbf{C}^\mathbf{J}$
  \cite{altenkirch-chapman-uustalu:2015}. A presheaf $P$ with a substitution
  monoidal structure $\Pair{\nu}{\varsigma}$ can be viewed as a relative monad
  on the functor $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
\end{remark}

>>>>

\begin{remark}
  A \emph{relative monad} on a functor $\Of{J}{\mathbf{J}\to\mathbf{C}}$ is a
  skew-monoid in the skew-monoidal structure induced by the functor category
  $\mathbf{C}^\mathbf{J}$ \cite{altenkirch-chapman-uustalu:2015}. In contrast to
  monoids, relative monads can also be understood as a generalization of the
  \emph{Kleisli structure} or \emph{extension system} presentation of monads. A
  presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  can be viewed as a relative monad on the functor
  $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
\end{remark}
